Finite-state morphological transducers for three Kypchak languages

### 2013-10-14 kipchak-lrec-2013/kipchak-paper.tex
more work
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48081 72bbbca6-d526-0410-a7d9-f06f51895060

We have evaluated the morphological analysers in two ways. The first was by calculating the naïve coverage and mean ambiguity 
on freely available corpora. The second was by performing an evaluation of precision and recall on some 
smaller, hand-validated test sets.

@@

\begin{table}
\begin{center}
\begin{tabular}{lr}
\textbf{Language} & - \\
\hline
Kazakh & - \\
Tatar & - \\
Kumyk & - \\
\hline
\end{tabular}
 \caption{Naïve coverage}
 \label{table:coverage}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{llrr}
\toprule
\textbf{Language} & \textbf{Corpus} & \textbf{Words} & \textbf{Coverage} \\
\midrule
\multirow{6}{*}{Kazakh} & wikipedia 2011& 850K &  - \\
	& Äwezov & 155K & - \\
	& RFERL 2010 & 3.2M & - \\
	& bible & 577K & - \\
	& quran & 107K & - \\\cline{2-4}
	& average & - & 90.5\% \\
\midrule
\multirow{5}{*}{Tatar} & wikipedia 2013 & 128K &  - \\
	& news 2005-2011 & 4.6M & - \\
	& new testament & 137K & - \\
	& quran & 165K & - \\
	& Aytmatov & 5K & - \\\cline{2-4}
	& average & - & 89.0\% \\
\midrule
\multirow{4}{*}{Kumyk} & yoldash & 287K &  - \\
	& new testament & 154K & - \\
	& book of Genesis & 28K & - \\\cline{2-4}
	& average & - & 88.0\% \\
\bottomrule
\end{tabular}
 \caption{Corpora used for coverage tests}
 \label{table:corpora}
\end{center}
\end{table}

>>>>

We have evaluated the morphological analysers in two ways. The first was by calculating the naïve coverage\footnote{Naïve coverage refers to the percentage of surface forms in a given corpora that receive at least one analysis.  Forms counted by this measure may have other analyses which are not delivered by the transducer.} and mean ambiguity 
on freely available corpora. The second was by performing an evaluation of precision and recall on some 
smaller, hand-validated test sets.

@@

% For kazakh+tatar tested the coverage of the analysers over 3 separate domains: encyclopaedic text, news and religion, 
% as there was no wikipedia for kumyk we just tested news and religion. The corpora were obtained from:
% Wikipedia:
% RFE/RL
% Yoldaš: 
% New testaments:

% kaz: kkwiki-20131006-pages-articles.xml.bz2
% tat:

\begin{table}
\begin{center}
\begin{tabular}{llrr}
\toprule
\textbf{Language} & \textbf{Corpus} & \textbf{Words} & \textbf{Coverage} \\
\midrule
\multirow{4}{*}{Kazakh} & Wikipedia 2013 &  -  &  - \\
	& RFE/RL 2010 & 3.2M & - \\
	& Bible & 577K & - \\\cline{2-4}
	& Average & - & 90.5\% \\
\midrule
\multirow{4}{*}{Tatar} & Wikipedia 2013 & 128K &  - \\
	& RFE/RL 2005--2011 & 4.6M & - \\
	& New Testament & 137K & - \\\cline{2-4}
	& Average & - & 89.0\% \\
\midrule
\multirow{3}{*}{Kumyk} & Yoldaš & 287K &  - \\
	& New Testament & 154K & - \\\cline{2-4}
	& Average & - & 90.1\% \\
\bottomrule
\end{tabular}
 \caption{Corpora used for naïve coverage tests}
 \label{table:corpora}
\end{center}
\end{table}

@@
